Title Goes Here

### 2020-02-25 paper/paper.tex
An additional forward reference in flowchart and improved spacing

\begin{tikzpicture}[node distance=2cm]
\node (start) [startstop] {Core from GHC};
  \node (tailrec) [process, below of=start, yshift=-0.5cm]{($D, T_{\ttt{f}}, T'_{\ttt{f}}$) Transform tail recursion of definitions that have a mark (when applicable)};
  \node (findmark) [process, below of=tailrec, yshift=-0.5cm]{($C^*$) Find marked expression and erase mark};
    \node (handlecase) [process, below of=findmark]{($C$) Mark scrutinee};
    \node (handleprim) [process, right of=handlecase, xshift=1.6cm]{($C$) Encode as EDSL primitive};
    \node (handleapp) [process, right of=handleprim, xshift=1.6cm]{($C$) Wrap with \ttt{Construct} and \ttt{ConstructAp}};

@@

    \node (onebranch) [process, below of=handlecase]{($B$) Transform one branch};
    \node (prodmatch) [process, below of=onebranch]{($P$) Transform one field in product match of current branch};
    \node (abstractvar) [process, below of=prodmatch]{($P, A$) Abstract the pattern variable of the field with \ttt{Lam} and \ttt{Var}};
    \node (markbody) [process, below of=abstractvar]{($P, M$) Mark branch body};
    \node (endstep) [process, below of=markbody, right of=markbody, xshift=1.6cm]{End of one transformation step};

>>>>

\begin{tikzpicture}[node distance=2cm]
\node (start) [startstop] {Core from GHC};
  \node (tailrec) [process, below of=start, yshift=-0.5cm]{($D, T_{\ttt{f}}, T'_{\ttt{f}}$) Transform tail recursion of definitions that have a mark (when applicable)};
  \node (findmark) [process, below of=tailrec, yshift=-0.5cm]{($C^*$) Find marked expression and erase mark};
    \node (handlecase) [process, below of=findmark]{($C, M$) Mark scrutinee};
    \node (handleprim) [process, right of=handlecase, xshift=1.6cm]{($C$) Encode as EDSL primitive};
    \node (handleapp) [process, right of=handleprim, xshift=1.6cm]{($C$) Wrap with \ttt{Construct} and \ttt{ConstructAp}};

@@

    \node (onebranch) [process, below of=handlecase]{($B$) Transform one branch};
    \node (prodmatch) [process, below of=onebranch]{($P$) Transform one field in product match of current branch};
    \node (abstractvar) [process, below of=prodmatch, yshift=-0.5cm]{($P, A$) Abstract the pattern variable of the field with \ttt{Lam} and \ttt{Var}};
    \node (markbody) [process, below of=abstractvar]{($P, M$) Mark branch body};
    \node (endstep) [process, below of=markbody, right of=markbody, xshift=1.6cm]{End of one transformation step};
